Handling String-Number Conversion in String Constraint Solving

### 2019-11-08 draft.tex
evaluation: revised tables.
working on product

\newcommand{\nat}{\mathbb{N}}
\newcommand{\todo}[1]{{\color{blue}TODO: #1}}
\newcommand{\lh}[1]{{\color{orange}Lukas: #1}}
\newcommand{\sti}[1]{\mbox{\textsf{toInt}($#1$)}}
\newcommand{\its}[1]{\mbox{\textsf{toStr}($#1$)}}
\newcommand{\varn}{\mbox{$\mathbb{V}_{\mathbb{Z}}$}}
\newcommand{\vars}{\mbox{$\mathbb{V}_{\Sigma^*}$}}
\newcommand{\cvars}{\mbox{$\mathbb{V}_{\Sigma_\epsilon}$}}
\newcommand{\pvars}{\mbox{$\mathbb{V}_{\sharp}$}}
\newcommand{\cvar}{\mbox{$V_{\Sigma_\epsilon}$}}
%\newcommand{\cvarone}{\mbox{$V^1_{\Sigma_\epsilon}$}}
%\newcommand{\cvartwo}{\mbox{$V^2_{\Sigma_\epsilon}$}}
\newcommand{\cvarone}{\mbox{$V_{\Sigma_\epsilon}$}}
\newcommand{\cvartwo}{\mbox{$V'_{\Sigma_\epsilon}$}}
\newcommand{\modelsof}[1]{[\![#1]\!]}
\newcommand{\true}{\mbox{$\mathsf{true}$}}
\newcommand{\false}{\mbox{$\mathsf{false}$}}
\newcommand{\enc}[1]{[\![#1]\!]}
%\newcommand{\parikhof}[1]{\mathit{Parikh}{(#1)}}
\newcommand{\parikhof}[1]{\mathbb{P}{(#1)}}
\newcommand{\parikhwof}[2]{|#1|_{#2}}
%\newcommand{\semof}[1]{||#1||}
\newcommand{\semof}[1]{\modelsof{#1}}
\newcommand{\decode}{\mathit{decode}}
\newcommand{\pformulaof}[1]{\Phi_{#1}}
\newcommand{\pim}{\alpha}
\newcommand{\syncop}{\Cap}
\newcommand{\syncof}[2]{A \syncop B}
\newcommand{\syncfof}[2]{\Psi_{\syncof {#1} {#2}}}
\newcommand{\syncfof}[2]{\Psi_{\syncof {#1} {#2}}}
\newcommand{\syncT}{T_\syncop}

@@

A \emph{finite automaton} is a tuple $(Q,T,\Sigma,q_0,q_m)$, where $Q$ is the set of \emph{states}, $T\subseteq Q\times (\Sigma\cup \{\epsilon\} )\times Q $ is the set of \emph{transitions}, $\Sigma$ is the alphabet, $q_0$ is the \emph{initial state}, and $q_m$ is the \emph{final state}. 
%The semantics of finite automaton is defined in the standard manner. 
We use $L(A)$ to denote the language of the automaton $A$, i.e., the set of accepted strings, defined in the standard manner.
\lh{If we later start technical talking about tings like runs then we should include this definition.}

@@

We introduce \emph{parametric flat automata} (PFA) that will be used to define patterns 
%for the string variable domain restriction. 
used by the under-approximation module to restrict the domain of string variables. 
Namely, an PFA is a finite automaton $A = (Q,T,\cvar,\st{0}{0},\st{m}{0})$ operating over the alphabet $\cvar$ of \emph{character variables}, 
and satisfying the following structural constraints:
\begin{enumerate}
	\item The final state $\st{m}{0}$ is reached from  the initial state $\st{0}{0}$ through a stright path of $m-1$ transitions $(\st{i}{0},v_i,\st{i+1}{0}) \in T$, $\st{i}{0} \in Q$ for $i\in[0,m-1]$. %, with pairwise distiand states $\st{i}{0} \in Q$ for $i\in[0,m-1]$.
	\item  
Each state $\st{i}{0}$ is the origin of a unique simple cycle of the length $l_i\in\mathbb{N}$, consisting of states $\st{i}{j-1} \in Q$ and transitions $(\st{i}{j-1}, \sym{i}{j-1}, \st{i}{j \bmod l_i})$ for $j\in [1,l_i]$. 
Notice that case when $l_i = 0$ is also admissible and means that there is no cycle on $q_i$.
%Assume that $\st{i}{0}$ is included in a cycle with $l_i$ states (includes $\st{i}{0}$). 
%For each $j\in [1,l_i]$, we have $\st{i}{j} \in Q$ and $(\st{i}{j-1}, \sym{i}{j-1}, \st{i}{j \bmod l_i})$. 
%(where $l_i = 0$ means that there is no cycle on $q_i$)
	\item Each variable in $\cvar$ appears on at most one transition (but $\epsilon$ transition can appear multiple times). 
\end{enumerate} 
\lh{TODO: decide whether we want epsilon trans, or perhaps additional constraints saying that a var equals epsilon or a character}
\begin{figure*}
	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
	\begin{tikzpicture} 
		\node[state,initial] (q0)  {$\st{0}{0}$};
		\node[state] (q1) [right = 3cm of q0] {$\st{1}{0}$};
		\node (q2) [right = 1.8cm of q1]{};
		\node (q3) [right = 1cm of q2]{};
		\node[state,accepting] (qm) [right = 1.8cm of q3] {$\st{m}{0}$};

@@

\begin{lemma}\label{lemma:parikh}
For an PFA $A$ and $x,y\in L(A)$ if $\parikhof x = \parikhof y$ then $x = y$. 
\end{lemma}
%
Indeed, since every variable appears on at most one transition, then the $\parikhof x$ value of all variables appearing within the same cycle is the same, and it is equal to the number of repetitions of that cycle in the accepting run. 
%
The accepting run on $x$ (and so $x$ itself) can thus be reconstructed from $\parikhof x$. \lh{say precisely how?}
%
For example, in the example of Figure~\ref{fig:sfa_def}, 
from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$. 
We may say that $\parikhof x$ is an encoding of $x$, and define the decoding function $\decode$ such that $\decode(\parikhof x) = x$.
It is well known that $\parikhof{A}$ can be computed in the form of a linear arithmetic formula  $\pformulaof{A}$ such that $\modelsof{\pformulaof A} = \parikhof{A}$, in time linear to the size of $A$ \cite{}.
\begin{lemma}\label{lemma:decx}
For a PFA $A$, $L(A) = \{\decode(\pim) \mid \pim\in\semof{\pformulaof A}\}$.
\end{lemma}

Since every string $w \in \semof{A}$ is obtained from a parametric string $x\in L(A)$ and an interpretation of character varriables $I:\cvar\rightarrow\Sigma_\epsilon$ such that $w = I(x)$, and since $x = \decode(\parikhof x)$, 
we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I$ and the Parikh image of the parametric string $x$ encode $w$. Lemma~\ref{lemma:parikh} also implies that two different strings are encoded by different united assignments (the Parikh image or the interpretation must be different), and hence we may extend the decoding function $\decode$ to united assignments so that $\decode(I \cup x) = w$.
Encodings of strings in $\semof{A}$ are encodings of strings of $L(A)$ paired with arbitrary interpretations of $\cvar$, 
hence $\semof A$ is characterised by models of $\parikhof A$ interpreted over variables $\cvar\cup\pvars$ (variables of $\cvar$  may have arbitrary values since $\parikhof A$ does not constraint them): 
%\begin{lemma}\ref{lemma:decw}
%For a PFA $A$, $\semof{A} = \{\decode(I\cup \pim) \mid \pim\in\semof{\pformulaof A} \land I:\cvar\rightarrow \Sigma_\epsilon\}$.
%\end{lemma}
\begin{lemma}
For a PFA $A$, $\semof{A} = \{\decode(I\cup \pim) \mid I\cup\pim\in\semof{\pformulaof A}_{\cvar\cup\pvars}\}$.
\end{lemma}

\paragraph{Synchronisation of PFA}
The following construction of the so called synchronisation formula of two PFA $A$ and $B$ is a crucial component of bulding overapproximations of string constraints. 
Synchronisation formula is a formula $\syncfof A B$ over $\pvars\cup\cvarone\cup \cvartwo$ encoding the semantic intersection $\semof A \cap \semof B$. Besides the intersection, it contains a more precise information about the synchronisation of $A$ and $B$, 
namely, it characterises the set of pairs of encodings $(I\cup \pim)\in \parikhof A$ and $(I'\cup \pim')\in\parikhof B$ such that 
$\decode(I\cup \pim) = \decode(I'\cup \pim')$ which constitute the intersection.

Assume that $A = (Q,T,\cvarone,q_i,q_f)$ and $B = (P,T',\cvartwo,p_i,p_f)$ are two SFA over disjoint sets of variables, $\cvarone \cap \cvartwo = \emptyset$. 
We build so called asynchronous product automaton $\syncof A B$ of $A$ and $B$ and then extract the formula $\syncfof A B$ from its Parikh image.
%
The product automaton uses $Q\times P$ as the set of states and $(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ as the alphabet. If a transition $((q_1,p_1), (v,v'),(q_2,p_2))$ is taken, it means the character variable $v$ and $v'$ should be assigned the same value and this value leads $A$ from state $q_1$ to state $q_2$ and $B$ from $p_1$ to $p_2$.

\begin{itemize}
\item If $(q_1,v,q_2) \in T$, then for all states $p\in P$, we have $((q_1,p),(v,\epsilon),(q_2,p))\in \syncT$.
\item If $(p_1,v,p_2) \in T'$, then for all states $q\in Q,((q,p_1)$, we have $(\epsilon,v),(q,p_2))\in \syncT$.
\item If $(q_1,v,q_2) \in T$ and $(p_1,v',p_2) \in T'$, then we have $((q_1,p_1),(v,v'),(q_2,p_2))\in \syncT$.
\end{itemize}	
The first two cases correspond to the situation when the character variable $v$ is assigned $\epsilon$. In such cases, only one automaton changes its state.
%
We compute a Presburger formula $\pformulaof {\syncof A B}$ over the set of variables $\{\#(v,v')\mid (v,v') \in \cvarone \times \cvartwo\}$ of the product automaton. 
%We use $\#v$ and $\#v'$ to denote the number of occurrences of $v_i$ and $v_i^{(j)}$, respectively. 
The following formulae establish the relation of the number of occurrences of symbols between the SFAs and the product automaton.
\begin{enumerate}
	\item for all $v \in \cvarone$, $\#(v) = \sum_{v' \in {\cvartwo \cup \{\epsilon\}}} \#{(v,v')}$   
	\item for all $v \in \cvartwo$, $\#(v) = \sum_{v' \in {\cvarone \cup \{\epsilon\}}} \#{(v',v)}$ 
\end{enumerate}

Then we add the following linear constraints to enforce  condition 1. and 2. required for the pair of symbolic string $(w_n, w_m)$ and $I$, i.e., $I(w_n) = I(w_m)$ and $I$ assign the same value to all versions of the same variable (we use $-1$ as the value of $\epsilon$). 
\begin{enumerate}
	\item for all $v\in \cvarone$ and $v'\in \cvartwo$, $\#{(v,v')}>0 \rightarrow (v=v')$, 
	\item for all $v\in \cvarone$, $\#{(v,\epsilon)}>0 \rightarrow (v=\epsilon)$, and
	Mitem for all $v\in \cvartwo$,$\#{(\epsilon,v)}>0 \rightarrow (v=\epsilon)$.
\end{enumerate}

The correctness of this construction is expressed by the following lemma
\begin{lemma}
For $\pim:\pvars\rightarrow \nat$, $\pim':\pvars\rightarrow\nat$, $I:\cvarone\rightarrow\Sigma$, $I':\cvartwo\rightarrow\Sigma$, 
we have $(I\cup\pim)\cup(I'\cup\pim')\in\semof \syncofof A B$ if and only if $\decode(I\cup\pim) = \decode(I'\cup\pim')$.
\end{lemma}
We actually have even something stronger, namely, that, $\syncofof A B$ has all possible allignments. How do I say this ... or do I have to say this?

@@

Such product automaton uses $Q\times P$ as the set of states and 
§$(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ as the alphabet. If a transition $((q_1,p_1), (v_i^{(j)},v_{i'}^{(j')}),(q_2,p_2))$ is taken, for some $i,j,i',j' \in \mathbb{N}$, it means the character variable $v_i$ and $v_{i'}$ (and so all of their indexed variants) should be assigned the same value and this value leads $A$ from state $q_1$ to state $q_2$ and $B$ from $p_1$ to $p_2$.

>>>>

\newcommand{\nat}{\mathbb{N}}
\newcommand{\todo}[1]{{\color{blue}TODO: #1}}
\newcommand{\lh}[1]{{\color{orange}Lukas: #1}}
\newcommand{\sti}[1]{\mbox{\textsf{toInt}($#1$)}}
\newcommand{\its}[1]{\mbox{\textsf{toStr}($#1$)}}
\newcommand{\varn}{\mbox{$\mathbb{V}_{\mathbb{Z}}$}}
\newcommand{\vars}{\mbox{$\mathbb{V}_{\Sigma^*}$}}
\newcommand{\cvars}{\mbox{$\mathbb{V}_{\Sigma_\epsilon}$}}
\newcommand{\pvars}{\mbox{$\mathbb{V}_{\sharp}$}}
%\newcommand{\cvar}{\mbox{$V_{\Sigma_\epsilon}$}}
%\newcommand{\cvarone}{\mbox{$V_{\Sigma_\epsilon}$}}
%\newcommand{\cvartwo}{\mbox{$V'_{\Sigma_\epsilon}$}}
\newcommand{\cvarone}{V}
\newcommand{\cvartwo}{V'}
\newcommand{\cvar}{V}
\newcommand{\pvar}{V_\#}
\newcommand{\pvarone}{V_\#}
\newcommand{\pvartwo}{V'_\#}
\newcommand{\modelsof}[1]{[\![#1]\!]}
\newcommand{\true}{\mbox{$\mathsf{true}$}}
\newcommand{\false}{\mbox{$\mathsf{false}$}}
\newcommand{\enc}[1]{[\![#1]\!]}
%\newcommand{\parikhof}[1]{\mathit{Parikh}{(#1)}}
\newcommand{\parikhof}[1]{\mathbb{P}{(#1)}}
\newcommand{\parikhwof}[2]{|#1|_{#2}}
%\newcommand{\semof}[1]{||#1||}
\newcommand{\semof}[1]{\modelsof{#1}}
\newcommand{\decode}[1]{\mathit{decode_{#1}}}
\newcommand{\parikhfof}[1]{\Phi_{\parikhof{#1}}}
\newcommand{\pim}{\alpha}
\newcommand{\syncop}{\Cap}
\newcommand{\syncof}[2]{#1 \syncop #2}
\newcommand{\syncfof}[2]{\Psi_{\syncof {#1} {#2}}}
\newcommand{\syncT}{T_\syncop}

@@

A \emph{finite automaton} is a tuple $(Q,T,\Sigma,q_i,q_f)$, where $Q$ is the set of \emph{states}, $T\subseteq Q\times \Sigma \times Q $ is the set of \emph{transitions}, $\Sigma$ is the alphabet, $q_0$ is the \emph{initial state}, and $q_m$ is the \emph{final state}. 
%The semantics of finite automaton is defined in the standard manner. 
A run of $A$ over a word $w = a_1\cdots a_n$ is a sequence of transition $(q_i)$
We use $L(A)$ to denote the language of the automaton $A$, i.e., the set of accepted strings, defined in the standard manner.
\lh{If we later start technical talking about tings like runs then we should include this definition.}

@@

We introduce \emph{parametric flat automata} (PFA) that will be used to define patterns 
%for the string variable domain restriction. 
used by the under-approximation module to restrict the domain of string variables. 
Namely, an PFA is a finite automaton $A = (Q,T,\cvar,\st{0}{0},\st{m}{0})$ operating over an alphabet $\cvar$ of \emph{character variables}, 
and satisfying the following structural constraints:
\begin{enumerate}
	\item The final state $\st{m}{0}$ is reached from  the initial state $\st{0}{0}$ through a stright path of $m-1$ transitions $(\st{i}{0},v_i,\st{i+1}{0}) \in T$, $\st{i}{0} \in Q$ for $i\in[0,m-1]$. %, with pairwise distiand states $\st{i}{0} \in Q$ for $i\in[0,m-1]$.
	\item  
Each state $\st{i}{0}$ is the origin of a unique simple cycle of the length $l_i\in\mathbb{N}$, consisting of states $\st{i}{j-1} \in Q$ and transitions $(\st{i}{j-1}, \sym{i}{j-1}, \st{i}{j \bmod l_i})$ for $j\in [1,l_i]$. 
Notice that case when $l_i = 0$ is also admissible and means that there is no cycle on $q_i$.
%Assume that $\st{i}{0}$ is included in a cycle with $l_i$ states (includes $\st{i}{0}$). 
%For each $j\in [1,l_i]$, we have $\st{i}{j} \in Q$ and $(\st{i}{j-1}, \sym{i}{j-1}, \st{i}{j \bmod l_i})$. 
%(where $l_i = 0$ means that there is no cycle on $q_i$)
	\item Each variable in $\cvar$ appears on at most one transition.% (but $\epsilon$ transition can appear multiple times). 
\end{enumerate} 
\lh{TODO: decide whether we want epsilon trans, or perhaps additional constraints saying that a var equals epsilon or a character}
\begin{figure*}
	\tikzset{state/.style={circle,draw=blue!50,fill=blue!20,
			thick,inner sep=0pt,minimum size=6mm}, initial text=$ $}
	\begin{tikzpicture} 
		\node[state,initial] (q0)  {$\st{0}{0}$};
		\node[state] (q1) [right = 3cm of q0] {$\st{1}{0}$};
		\node (q2) [right = 1.8cm of q1]{};
		\node (q3) [right = 1cm of q2]{};
		\node[state,accepting] (qm) [right = 1.8cm of q3] {$\st{m}{0}$};

@@

\begin{lemma}\label{lemma:parikh}
For an PFA $A$ and $x,y\in L(A)$ if $\parikhof x = \parikhof y$ then $x = y$. 
\end{lemma}
%
Indeed, since every variable appears on at most one transition, then the $\parikhof x$ value of all variables appearing within the same cycle is the same, and it is equal to the number of repetitions of that cycle in the accepting run. 
%
The accepting run on $x$ (and so $x$ itself) can thus be reconstructed from $\parikhof x$. \lh{say precisely how?}
%
For example, in the example of Figure~\ref{fig:sfa_def}, 
from $\parikhwof x {v_0} = \parikhwof x {v_1} = \cdots = \parikhwof x {v_{m-1}}=1$ and $\parikhwof x {v^0_1}=\parikhwof x {v^1_1}=\parikhwof x {v^2_1}=2$ we derive that $x=v_0(v^0_1v^1_1v^2_1)^2v_1\cdots v_{m-1}$. 
We may say that $\parikhof x$ is an encoding of $x$, and define the decoding function $\decode A$ such that $\decode A(\parikhof x) = x$.
It is well known that $\parikhof{A}$ can be computed in the form of a linear arithmetic formula  $\parikhfof{A}$ such that $\modelsof{\parikhfof A} = \parikhof{A}$, in time linear to the size of $A$ \cite{}.
\begin{lemma}\label{lemma:decx}
For a PFA $A$, $L(A) = \{\decode A(\pim) \mid \pim\in\semof{\parikhfof A}\}$.
\end{lemma}

Since every string $w \in \semof{A}$ is obtained from a parametric string $x\in L(A)$ and an interpretation of character varriables $I:\cvar\rightarrow\Sigma_\epsilon$ such that $w = I(x)$, and since $x = \decode A(\parikhof x)$, 
we may say that the assignment $I \cup \parikhof x$ uniting the interpretation $I$ and the Parikh image of the parametric string $x$ encodes $w$. Lemma~\ref{lemma:parikh} also implies that two different strings are encoded by different united assignments (the Parikh image or the interpretation must be different), and hence we may extend the decoding function $\decode A$ to united assignments so that $\decode A(I \cup x) = w$.
Encodings of strings in $\semof{A}$ are encodings of parametric strings of $L(A)$ paired with arbitrary interpretations of character variables $\cvar$, 
hence $\semof A$ is characterised by models of $\parikhof A$ interpreted over variables $\cvar\cup\pvar$ (variables of $\cvar$  may have arbitrary values since $\parikhof A$ does not constraint them), we may say that 
%\begin{lemma}\ref{lemma:decw}
%For a PFA $A$, $\semof{A} = \{\decode(I\cup \pim) \mid \pim\in\semof{\parikhfof A} \land I:\cvar\rightarrow \Sigma_\epsilon\}$.
%\end{lemma}
 $$\semof{A} = \{\decode A(I\cup \pim) \mid I\cup\pim\in\semof{\parikhfof A}_{\cvar\cup\pvar}\}$$
where $\semof{\parikhfof A}_{\cvar\cup\pvar}$ are models of $\parikhfof A$, assignments to $\pvar$, united with arbitrary interpretations of $\cvar$ \lh{this is ugly}.

\paragraph{Synchronisation of PFA}
The following construction of the so called synchronisation formula of two PFA $A$ and $A'$ is a crucial component of building overapproximations of string constraints. 
Synchronisation formula is a formula $\syncfof A {A'}$ over $\pvarone\cup\pvartwo\cup\cvarone\cup \cvartwo$ encoding the semantic intersection $\semof A \cap \semof {A'}$. Besides the intersection, it contains a more precise information about the synchronisation of $A$ and ${A'}$, 
namely, it characterises the set of pairs of encodings $(I\cup \pim)\in \parikhof A$ and $(I'\cup \pim')\in\parikhof {A'}$ such that 
$\decode A(I\cup \pim) = \decode {A'}(I'\cup \pim')$.% which constitute the intersection.

Assume that $A = (Q,T,\cvarone,q_i,q_f)$ and ${A'} = (Q',T',\cvartwo,q_i',q_f')$ are two SFA over disjoint sets of variables, $\cvarone \cap \cvartwo = \emptyset$. 
We build so called asynchronous product automaton $\syncof A {A'}$ of $A$ and ${A'}$ and then extract the formula $\syncfof A {A'}$ from its Parikh image.
%
Such product automaton uses $Q\times Q'$ as the set of states and 
%$(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ 
$\cvarone_\epsilon\times\cvartwo_\epsilon$
as the alphabet. 
%
Every accepting run of $\syncof A {A'}$ \lh{define run as a sequence of transitions etc} corresponds to an accepting run of $A$ and an accepting run of ${A'}$, and the word accepted by the run of $\syncof A {A'}$ implies a set of constraints on $\pvarone\cup\pvartwo\cup\cvarone\cup\cvartwo$ under which the word accepted by $A$ has the same semantics as the word accepted by ${A'}$.
%
Particularly, if a transition $((q_1,q_1'), (v,v'),(q_2,q_2'))$ is taken, it means the character variable $v$ and $v'$ should be assigned the same value and this value leads $A$ from state $q_1$ to state $q_2$ and ${A'}$ from $q_1'$ to $q_2'$.
%
If a transition $((q_1,q_1'), (v,\epsilon),(q_2,q_1'))$ is taken, then it means that the character variable $v$ should be assigned $\epsilon$, $A$ may transition under $v$ to $q_1$ and ${A'}$ stays in the same state, as a response to $A$s reading epsilon may as well be taking no action. Symmetrically, ${A'}$ might read a variable $v$ assigned $\epsilon$ and $A$ may stay.

Formally, the product automaton is a tuple $\syncof A {A'} = (Q\times Q', \syncT, \cvarone_\epsilon \times \cvartwo_\epsilon, (q_i,q_i'),(q_f,q_f'))$, where the transition relation $\syncT$ is the minimal set satisfying the following:
%
\begin{itemize}
\item If $(q_1,v,q_2) \in T$ and $(q_1',v',q_2') \in T'$, then we have $((q_1,q_1'),(v,v'),(q_2,q_2'))\in \syncT$.
\item If $(q_1,v,q_2) \in T$, then for all states $q'\in Q'$, we have $((q_1,q'),(v,\epsilon),(q_2,q'))\in \syncT$.
\item If $(q_1',v',q_2') \in T'$, then for all states $q\in Q$, we have $((q,q_1'),(\epsilon,v'),(q,q_2'))\in \syncT$.
\end{itemize}	
%
Next, we define the set of constraints that extract from $\syncof A {A'}$ pairs of united assignments (encodings of strings over $\Sigma$) that encode the same string. 
We start with the Parikh formula $\parikhfof {\syncof A {A'}}$ of $\syncof A {A'}$ over the set of variables $\{\#(v,v')\mid (v,v') \in \cvarone_\epsilon \times \cvartwo_\epsilon\}$ of the product automaton and conjoin it with the following restricting constraints. 
%We use $\#v$ and $\#v'$ to denote the number of occurrences of $v_i$ and $v_i^{(j)}$, respectively.

The first restricting constraint establishes the relation of between the Parikh image of a word accepted by $\syncof A {A'}$ and the Parikh images of the corresponding parametric strings accepted by $A$ and ${A'}$:
$$ \Psi_{\#} = 
\left(\bigwedge_{v\in\cvarone}\#v = \sum_{x' \in \cvartwo_\epsilon} \#{(v,x')}\right)
\land
\left(\bigwedge_{v'\in\cvartwo} \#v' = \sum_{x \in \cvarone_\epsilon} \#{(x,v')}\right)
$$
Notice that $x,x'$ are either variables or $\epsilon$.
%\begin{enumerate}
%	\item for all $v \in \cvarone$, $\#(v) = \sum_{v' \in \cvartwo} \#{(v,v')}$   
%	\item for all $v \in \cvartwo$, $\#(v) = \sum_{v' \in \cvarone} \#{(v',v)}$ 
%\end{enumerate}

Then we add the following linear constraints to enforce that the decodings of the models are indeed the same, 
% condition 1. and 2. required for the pair of symbolic string $(w_n, w_m)$ and $I$, i.e., $I(w_n) = I(w_m)$ and $I$ assign the same value to all versions of the same variable (we use $-1$ as the value of $\epsilon$). 
$$ \Psi_= =
\bigwedge_{x\in\cvarone_\epsilon,x'\in\cvartwo_\epsilon} \#(x,x')>0 \rightarrow (x=x')
$$
%\begin{enumerate}
%	\item for all $v\in \cvarone$ and $v'\in \cvartwo$, $\#{(v,v')}>0 \rightarrow (v=v')$, 
%	\item for all $v\in \cvarone$, $\#{(v,\epsilon)}>0 \rightarrow (v=\epsilon)$, and
%	\item for all $v\in \cvartwo$,$\#{(\epsilon,v')}>0 \rightarrow (v'=\epsilon)$.
%\end{enumerate}

The synchronisation formula is the conjunction 
$$
\syncfof A {A'} = \parikhfof{\syncof A {A'}} \land \Psi_{\#} \land \Psi_=
$$
The correctness of this construction is expressed by the following lemma
%\begin{lemma}
%For $\pim:\pvarone\rightarrow \nat$, $\pim':\pvartwo \rightarrow\nat$, $I:\cvarone\rightarrow\Sigma$, $I':\cvartwo\rightarrow\Sigma$, 
%we have $(I\cup\pim)\cup(I'\cup\pim')\in\semof {\syncfof A {A'}}$ if and only if $\decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')$.
%\end{lemma}

\begin{lemma}
 $\semof {\syncfof A {A'}} = \{(I\cup\pim)\cup(I'\cup\pim') \mid \decode A(I\cup\pim) = \decode {A'}(I'\cup\pim')\}$. 
\end{lemma}

We actually have even something stronger, namely, that, $\syncfof A {A'}$ has all possible allignments. How do I say this ... or do I have to say this?

@@

Such product automaton uses $Q\times P$ as the set of states and 
%$(\cvarone \cup \{\epsilon\}) \times (\cvartwo \cup \{\epsilon\} )$ 
$\cvarone\times\cvartwo$
as the alphabet. If a transition $((q_1,p_1), (v,v'),(q_2,p_2))$ is taken, it means the character variable $v$ and $v'$ should be assigned the same value and this value leads $A$ from state $q_1$ to state $q_2$ and $B$ from $p_1$ to $p_2$.
